---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# dopcalc

[![Travis-CI Build Status](https://travis-ci.org/pboesu/dopcalc.svg?branch=master)](https://travis-ci.org/pboesu/dopcalc)
[![Coverage Status](https://img.shields.io/codecov/c/github/pboesu/dopcalc/master.svg)](https://codecov.io/github/pboesu/dopcalc?branch=master)
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)

The goal of dopcalc is to forecast or hindcast GPS satellite constellations and associated positioning precision metrics for arbitrary locations. Use cases include GPS mission planning, i.e. determining times of good GPS coverage at a survey location, or post-hoc precision estimation for GPS data that lacks signal quality information.

The initially targeted use-case is focussed on seabirds at sea, so horizon shading by terrain or the built environment is currently not considered. `r #(but see library(horizon) and/or GRASS modules r.horizon and r.obstruction for possible solutions to this. Neither appears to allow for flight height, though)`

Calculations are based on GPS almanac data. Optional automatic downloads of the required almanac files from the US Coast Guard Navigation Center when necessary are part of the planned functionality.

The R package draws on previous work by others, in particular [Master's thesis]

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```
