---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# dopcalc

[![Travis-CI Build Status](https://travis-ci.org/pboesu/dopcalc.svg?branch=master)](https://travis-ci.org/pboesu/dopcalc)
[![Coverage Status](https://img.shields.io/codecov/c/github/pboesu/dopcalc/master.svg)](https://codecov.io/github/pboesu/dopcalc?branch=master)

The goal of dopcalc is to forecast or hindcast GPS satellite constellations and associated positioning precision metrics. Use cases include GPS mission planning, i.e. determining times of good GPS coverage at a survey location, or post-hoc precision estimation for GPS data that lacks signal quality information.

Calculations are based on GPS almanac data, which is automatically obtained from the US Coast Guard Navigation Center when necessary.

The R package draws heavily on previous work by others, in particular [thesis]

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```
